%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kyle}{Rubenok}
{\urlstyle{same}
Github:// \href{https://github.com/krubenok}{\custombold{krubenok}} | LinkedIn://  \href{https://www.linkedin.com/in/krubenok}{\custombold{krubenok}} \\
\href{mailto:kyle@rubenok.ca}{kyle@rubenok.ca} | 647-500-8391}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{McGill University}
\descript{Bachelor's Degree}
\vspace{\topsep}
\begin{tightemize}
\item Major in Computer Science
\item Minor in Economics
\end{tightemize}
\location{Expected Dec 2019 | Montreal, QC}
\sectionsep


\subsection{Toronto French School}
\descript{International Baccalaureate Diploma}
\location{Graduated 2015 | Toronto, ON}
Ontario Scholar\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%     RELOCATED TO HEADER DUE TO ONLY HAVING TWO OF NOTE.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Links} 
% Github:// \href{https://github.com/krubenok}{\custombold{krubenok}} \\
% LinkedIn://  \href{https://www.linkedin.com/in/krubenok}{\custombold{krubenok}} \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\vspace{\topsep}
\begin{tightemize}
\item Intro to Computer Science
\item Algorithms and Data Structures
\item Software Systems
\item Intro to Computer Systems
\item Discrete Structures
\item Operating Systems
\item Functional Programming
\item Intro to AI
\item Theory of Computation
\item Software Design
\item Databases
\item Robotics
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Comfortable:}
Java \textbullet{} Python \textbullet{} HTML\\
\LaTeX\ \textbullet{} CSS \textbullet{} Bash\\ 
\location{Familiar:}
Assembly \textbullet{} C\\
JavaScript \textbullet{} OCAML\\
\sectionsep
\subsection{Technical}
Containerisation\\
Virtualized Environments\\ 
Dev Ops\\
AB Testing\\
UX Prototyping\\
Enterprise Networking\\
Systems Administration\\
\sectionsep
\subsection{Certifications}
\vspace{\topsep}
\begin{tightemize}
\item Apple Certified Macintosh Technician
\item G-Suite Certified Administrator
\item Cisco Meraki Network Associate
\end{tightemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Microsoft}
\descript{| Program Manager (Intern)}
\location{May - Aug 2018, May - Aug 2019 | Redmond, WA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Worked on Enterprise Mobility Management team to develop features for SCCM serving over 130 Million end users.
\item Designed Management Insights Dashboard in partnership with Engineers, Sales and Customers to improve deployment practices for admins.
\item Developed cost calculator for Cloud Management Gateway using machine learning on usage history to increase feature adoption of a multi-million dollar Azure opportunity.
\end{tightemize}
\sectionsep

\runsubsection{Cisco}
\descript{| Consulting Systems Engineer (Intern)}
\location{May – Aug 2017, May - Aug 2016 | Toronto, ON}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed chat bot interfaces for internal and external tools to deliver critical alerts more effectively.
\item Led internal evangelism of WebEx Teams platform increasing internal user base by 35\%.
\end{tightemize}
\sectionsep

\runsubsection{Penguinleaf Technologies}
\descript{| Co-Founder}
\location{June 2014 – Present}
\begin{tightemize}
\item Co-Founded a full service technology consulting business specializing in cloud managed service
\item Developed a scalable services offering to grow client list from 3 to over 25 in 1 year serving over 3000 end users.
\item Gained valuable cross functional business skills working with clients from all sectors and maintaining profitability.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LEADERSHIP
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership}
\runsubsection{Computer Science Undergraduate Society}
\descript{| President}
\location{May 2017 – May 2019 | Montreal, QC}
\begin{tightemize}
\item Representative of over 1800 Computer Science students at McGill to administration, recruiters, and student government. 
\item Co-Created a peer tutoring helpdesk with over 40 tutors open daily serving 350+ help requests a week.
\end{tightemize}
\sectionsep

\runsubsection{HackMcGill}
\descript{| Co-Director}
\location{May 2017 – May 2019 | Montreal, QC}
\begin{tightemize}
\item Lead planning of McGill's premier student hackathon, McHacks with over 600 participants.
\item Developed new sponsorship process leading to more sponsors and a 90\%YOY increase in budget.
\item Lead development of in-house open source tools to manage sponsors, hackers and registration.
\end{tightemize}
\sectionsep

\runsubsection{Students' Society of McGill University}
\descript{| Board of Directors}
\location{May 2018 – Present | Montreal, QC}
\begin{tightemize}
\item Supervise the administration and operations of an 8+ Million Dollar non-profit organization providing services to McGill Students. 
\item Member of Accountability, Finance, HR and Nominating Committees. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2017     & 2nd Place Intern Technical Sales Competition, Cisco\\
% 2015     & Parents Association Award for Community Service\\
% 2015     & Edward A. Tory Award (Over 90\% Average upon graduation\\
% 2014     & Rookie Coach of The Year, Beaver Valley\\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
